Untitled

### 2022-10-05 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
Final edits on supp mat

---
#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Covariation among reproductive traits in flowering plants determine interactions with floral visitors}

@@

## Covariation among reproductive traits in flowering plants determine interactions with floral visitors

>>>>

---
#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Covariation among reproductive traits in flowering plants shape their interactions with pollinators}

@@

## Covariation among reproductive traits in flowering plants shape their interactions with pollinators
